Fig3

### 2020-05-26 analysis/figure-3.Rmd
better fig 3

```

@@

c1 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 DEGs, low vs. high PRL") 
c2 <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes in WGCNA module with PRL") 
c3 <- plotcorrplot(cancergenes, NULL) + theme(legend.position = "right") + labs(subtitle = "Breast, ovary, & piuitary cancer genes") 
c <- plot_grid(c1,c2,c3, nrow = 1, labels = c("D", "E", "F"), label_size = 8, rel_widths = c(1,1,1.3))

>>>>

## number of genes total vs plotted

eggchickdf %>% filter(tissue == "pituitary") %>% nrow()
hilodf %>% filter(tissue == "pituitary") %>% nrow()
length(WGCNAgenes)
```

@@

c1 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 DEGs, low vs. high PRL") 
c2 <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes in WGCNA module with PRL") 
c3 <- plotcorrplot(cancergenes, NULL) + theme(legend.position = "right") + labs(subtitle = "Breast, ovary, & piuitary cancer genes") 
c <- plot_grid(c1,c2,c3, nrow = 1, labels = c("D"), label_size = 8, rel_widths = c(1,1,1.3))
